---
title: "presentation"
author: "Yujia_Wang"
date: "10/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment=NA, echo = FALSE, message = FALSE, warning=FALSE, margin=TRUE)

#opts_chunk$set(comment=NA, echo = FALSE, message = FALSE, warning=FALSE, margin=TRUE)

#opts_chunk$set(echo = FALSE, message = FALSE, warning=FALSE, margin=TRUE)

source("wrangling_code.R")
```

I choose co2 intensity of economic output and gdp total yearly growth. 
The former is the amount of CO2 produced to develop the economy. 
The latter is an important indicator to measure the economy of a country, and its annual growth represents the level of economic progress of the country.
I selected 2000 to 2012 data from the United States and China.

```{r}
#Because I want to add interpretation in each plot, so I don't use source("visualization_function.R"). 
#The "function" is in "visualization_function.R" and doesn't show in "presentation.rmd".

#plot1
color=ifelse(tidy_use$country=="China","red","blue")
group<-ifelse(tidy_use$country=="China",1,2)
plot1<-ggplot(data=tidy_use) +
  geom_line(aes(x=year,y=gdp,colour=country,group=group))+
  geom_point(aes(x=year,y=gdp,colour=color))+
  labs(x="YEAR",
       y="GDP",
       subtitle="Line Chart: US vs China of GDP",
       caption="Source:Gapminder")
plot1
```

According to plot 1, the GDP growth rate of US is lower than that of China under most circumstances.
From 2013 to 2015, the U.S. reversed the trend.
In both countries the trend is upward.


```{r}
#plot2
plot2<-ggplot(data=tidy_use) +
  geom_bar(aes(x=year,y=gdp,fill=country),position="dodge",stat="identity")+
  labs(x="YEAR",
       y="GDP",
       subtitle="Bar graph: US vs China of GDP",
       caption="Source: Gapminder")
plot2
```

According to plot 2, the US's overall GPD growth is lower than China's.
According to the US, negative growth appeared in 2007 and 2008.
The US's GDP growth is leveling off and China's is rising.


```{r}
#plot3
plot3<-ggplot(data=tidy_use, aes(x=co2, fill=country)) +
  geom_density(alpha=0.3)
plot3
```

According to plot 3, the density of CO2 output in China is higher than that in the United States.
The U.S. is between 0.3 and 0.4, and China's is between 0.7 and 0.8.
So China produces more CO2 in economic fields than the US.

In conclusion, China consumes more CO2 in economic construction, so that China's GDP growth is higher than the US's. 


