---
title: "presentation"
author: "Yujia_Wang"
date: "10/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment=NA, echo = FALSE, message = FALSE, warning=FALSE, margin=TRUE)

#opts_chunk$set(comment=NA, echo = FALSE, message = FALSE, warning=FALSE, margin=TRUE)

#opts_chunk$set(echo = FALSE, message = FALSE, warning=FALSE, margin=TRUE)

library(readxl)

library("xlsx")

library(tidyverse)

library(tidyr)
library(dplyr)

library(reader)
```

```{r}
setwd("C:/Users/L/Downloads")

gdp_all<-read_xlsx("gdp_total_yearly_growth.xlsx")
co2_all<-read_excel("co2_intensity_of_economic_output_kg_co2_per_2011_ppp_of_gdp.xlsx")

#as_tibble(gdp_all)
#as_tibble(co2_all)

gdp<-select(gdp_all,"country","2000":"2012")
co2<-select(co2_all,"country","2000":"2012")

##########################################################

gdp_tidy<- gdp %>% 
  pivot_longer(!country,names_to="year",values_to="gdp")

co2_tidy<- co2 %>% 
  pivot_longer(!country,names_to="year",values_to="co2")

tidy<- co2_tidy %>% inner_join(gdp_tidy)

tidy_use<- filter(tidy,country=="United States" | country=="China")

##########################################################

#function1
plot1<-function(x){
  try(if(!is.data.frame(x)) stop("Input data must be a data frame."))
  
  color=ifelse(x$country=="China","red","blue")
  group<-ifelse(x$country=="China",1,2)
  plota<-ggplot(data=x) +
    geom_line(aes(x=year,y=gdp,colour=country,group=group))+
    geom_point(aes(x=year,y=gdp,colour=color))+
    labs(x="YEAR",
         y="GDP",
         subtitle="Line Chart: US vs China of GDP",
         caption="Source:Gapminder")
  return(plota)
}
#input: plot1(tidy_use)

#function2
plot2<-function(x){
  try(if(!is.data.frame(x)) stop("Input data must be a data frame."))
  
  plotb<-ggplot(data=x) +
    geom_bar(aes(x=year,y=gdp,fill=country),position="dodge",stat="identity")+
    labs(x="YEAR",
         y="GDP",
         subtitle="Bar graph: US vs China of GDP",
         caption="Source: Gapminder")
  return(plotb)
}
#input: plot2(tidy_use)


#function3
plot3<-function(x){
  try(if(!is.data.frame(x)) stop("Input data must be a data frame."))
  
  plotc<-ggplot(data=x, aes(x=co2, fill=country)) +
    geom_density(alpha=0.3)
  return(plotc)
}
#input: plot3(tidy_use)

#This task is in Assignment 1 "hand_fuction"

##########################################################

#plot1
color=ifelse(tidy_use$country=="China","red","blue")
group<-ifelse(tidy_use$country=="China",1,2)
plot1<-ggplot(data=tidy_use) +
  geom_line(aes(x=year,y=gdp,colour=country,group=group))+
  geom_point(aes(x=year,y=gdp,colour=color))+
  labs(x="YEAR",
       y="GDP",
       subtitle="Line Chart: US vs China of GDP",
       caption="Source:Gapminder")
plot1
```

According to plot 1, the GDP growth rate of US is lower than that of China under most circumstances.
From 2013 to 2015, the U.S. reversed the trend.
In both countries the trend is upward.


```{r}
#plot2
plot2<-ggplot(data=tidy_use) +
  geom_bar(aes(x=year,y=gdp,fill=country),position="dodge",stat="identity")+
  labs(x="YEAR",
       y="GDP",
       subtitle="Bar graph: US vs China of GDP",
       caption="Source: Gapminder")
plot2
```

According to plot 2, the US's overall GPD growth is lower than China's.
According to the US, negative growth appeared in 2007 and 2008.
The US's GDP growth is leveling off and China's is rising.


```{r}
#plot3
plot3<-ggplot(data=tidy_use, aes(x=co2, fill=country)) +
  geom_density(alpha=0.3)
plot3
```

According to plot 3, the density of CO2 output in China is higher than that in the United States.
The U.S. is between 0.3 and 0.4, and China's is between 0.7 and 0.8.
So China produces more CO2 in economic fields than the US.

In conclusion, China consumes more CO2 in economic construction, so that China's GDP growth is higher than America's. 


